Differential Expression - MSSM-Penn-Pitt - ACC - Sex

### 2020-07-30 individual-cohorts/MSSM-Penn-Pitt_ACC_DE.Rmd
fix DE data.frame

# Get differential expression
DE = topTable(FIT.CONTR, coef= "L1", number = Inf) %>% 
    rownameToFirstColumn('gene_id') %>%
    left_join(backgroundGenes)

>>>>

# Get differential expression
DE = lapply(glue::glue("L1"), function(i, FIT){
  topTable(FIT, coef=i, number = Inf) %>%
    rownameToFirstColumn('gene_id') %>% 
    left_join(backgroundGenes)
}, FIT.CONTR)
